Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-06-24 manuscript/manuscript.Rmd
improving meta analysis description

The present study is highly comparable in goal and design to a previous study (Hardwicke et al. 2018), presenting an opportunity to synthesize their estimates of analytic reproducibility in psychology. To this end, we used random-effects models to meta-analyze the raw proportion estimates of article-level analytic reproducibility for the two studies, separately before and after original authors were contacted.

@@

```{r scatterPlot, fig.cap="Scatterplot showing reanalysis p-values as a function of reported p-values, classified by reproducibility outcome. Axes are on a log scale. For display purposes, 41 values below 0.001 are not shown.", fig.path="figs/"}
source(here('analysis','plot_reproScatter.R')) # build plot
scatterPlot # show plot
```
```{r}
source(here('analysis','meta_analysis.R'))
```

@@

Some reproducibility issues were resolved through involvement of original authors, however, relying on such assistance is not ideal for several reasons: (1) it substantially increases the workload and time investment, both for researchers attempting to re-use data and for original authors; (2) important details about and materials related to the study are more likely to be forgotten or misplaced over time, reducing the ability of authors to assist [@vines2014]; (3) authors may be unwilling or unable to respond, as was the case for three of the articles we examined. Author involvement highlighted that non-reproducibility was often caused by unclear, incomplete, or incorrect reporting of analytic procedures in the original papers, issues which could often be resolved through the provision of additional information or clarifications beyond what was previously reported. In other cases, authors informed us of errors in shared data files or analysis scripts, suggesting that at some stage the original data, analyses, and research report had become decoupled. For many issues, neither we nor the original authors could reproduce the target values and the causal locus of non-reproducibility remained unidentified; it was no longer possible to reconstruct the original analysis pipeline.

@@

Although journal policy is potentially helpful for incentivisation and verification, the reproducibility of a scientific manuscript is fundamentally within the control of its authors. Fortunately, a variety of tools are now available that allow for the writing of entirely reproducible research reports in which data, analysis code, and research reports are intrinsically linked [e.g., @vuorre2020]. Detailed guidance on data sharing, data management, and analytic reproducibility is available to support psychological scientists seeking to improve these practices in their own research [@klein2018].  The present manuscript is an illustration of these practices in action (https://doi.org/10.24433/CO.6557927.v1). It should be noted that ensuring the reproducibility of a scientific manuscript requires a non-trivial time investment. Continued development of user-friendly tools that facilitate reproducibility and dedicated training may help to reduce this burden. Additionally, the costs of ensuring reproducibility could be offset by the benefits of improved workflow efficiency, error detection and mitigation, and potential for data re-use.

>>>>

The present study is highly comparable in goal and design to a previous study (Hardwicke et al. 2018), presenting an opportunity to synthesize their estimates of analytic reproducibility in psychology. To this end, we used random-effects models with inverse-variance weighting to meta-analyze the raw proportion estimates of article-level analytic reproducibility for the two studies, separately before and after original authors were contacted [@schwarzer2015].

@@

```{r scatterPlot, fig.cap="Scatterplot showing reanalysis p-values as a function of reported p-values, classified by reproducibility outcome. Axes are on a log scale. Dashed lines represent the typical 0.05 threshold for statistical significance. For display purposes, 41 values below 0.001 are not shown.", fig.path="figs/"}
source(here('analysis','plot_reproScatter.R')) # build plot
scatterPlot # show plot
```
```{r}
source(here('analysis','meta_analysis.R'))
```

@@

Some reproducibility issues were resolved through involvement of original authors, however, relying on such assistance is not ideal for several reasons: (1) it substantially increases the workload and time investment, both for researchers attempting to re-use data and for original authors; (2) important details about and materials related to the study are more likely to be forgotten or misplaced over time, reducing the ability of authors to assist [@vines2014]; (3) authors may be unwilling or unable to respond, as was the case for three of the articles we examined. Author involvement highlighted that non-reproducibility was often caused by unclear, incomplete, or incorrect reporting of analytic procedures in the original papers, issues which could often be resolved through the provision of additional information or clarifications beyond what was previously reported. In other cases, authors informed us of errors in shared data files or analysis scripts, suggesting that at some stage the original data, analyses, and research report had become decoupled. In some cases, neither we nor the original authors could reproduce the target values and the causal locus of non-reproducibility remained unidentified; it was no longer possible to reconstruct the original analysis pipeline.

@@

Although journal policy is potentially helpful for incentivisation and verification, the reproducibility of a scientific manuscript is fundamentally within the control of its authors. Fortunately, a variety of tools are now available that allow for the writing of entirely reproducible research reports in which data, analysis code, and research reports are intrinsically linked [e.g., @vuorre2020]. It should be noted that ensuring the reproducibility of a scientific manuscript requires a non-trivial time investment and presently, there is room for improvement in the data management and analysis practices adopted by psychological researchers [e.g., @borghi2020]. Continued development of user-friendly tools that facilitate reproducibility and dedicated training may help to reduce this burden. Additionally, the costs of ensuring reproducibility could be offset by the benefits of improved workflow efficiency, error detection and mitigation, and potential for data re-use. Detailed guidance on data sharing, data management, and analytic reproducibility is available to support psychological scientists seeking to improve these practices in their own research [@klein2018]. The present manuscript is an illustration of these practices in action (https://doi.org/10.24433/CO.6557927.v1).
